Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2023-03-13 reports/revision_letter.Rmd
Revise to match NHB checklist

We agree with the reviewer that the term 'screen time' is problematic as it fails to acknowledge the diversity of experiences screens provide.
Indeed, our motivation for conducting this review was to counter this narrative in the literature.
To do this, it was necessary to invoke the concept of 'screen time'.
As our results show, the influence of screen time on children is less a function of a physical screen, and more a function of the activity that the screen provides.
But, we feel that a review such as this is needed in order to emphasise the diverse influence that screens can have. 
If the results are not collated into a single place, it is difficult to see how the field will begin to progress away from 'screen time' as a concept. 
We have included this in the *Implications for Future Research* section:

@@

@@

The reviewer was pointing to the following quote from the *Lancet*: "Our understanding of the benefits, harms, and risks of our rapidly changing digital landscape is sorely lacking.".
It is not that the evidence is lacking, per se, but that our *understanding* is weak.
Our understanding is lacking partly because benefits of screen time (as seen in some educational literature) and reviewed separately from harms.
Our review aims to address this (see also Reviewer 1, \comment{r1_2}).
We think synthesising the trade-offs in one review can help us understand when screen time might be associated with good/poor outcomes, helping to better understand why.

@@

We appreciate it is not a direct contrast to compare overall limits of screen time against deleterious effects of screen time over 3-4 hours. As a result, we have removed the words 'in contrast':

@@

We agree that the relationship between some outcomes and screen time may not always be linear.
However, our previous research (e.g., 10.1186/s12966-019-0881-7) looking at a range of health and education outcomes in a high-quality dataset found little evidence for curvilinear relationships.
We therefore felt that the linear model was appropriate for the majority of the outcomes in this review.
Additionally, almost none of the reviews we included reported information that would allow us to calculate non-linear effects.
We agree that this is an important limitation though, and have added information on this to the *Discussion* section:

@@

We agree both guidelines focus on merely reducing recreational screen time and have removed "in all instances".
Even within recreational screen time, however, our findings do not support guidelines which focus just on minimisation. 
Video games, for example, are a recreational form of screen time which appear to have some benefits for educational and cognitive outcomes.

>>>>

We agree with the reviewer that the term 'screen time' is problematic as it fails to acknowledge the diversity of experiences screens provide.
Indeed, our motivation for conducting this review was to counter this narrative in the literature.
To do this, it was necessary to invoke the concept of 'screen time'.
As our results show, the influence of screen time on children is less a function of a physical screen, and more a function of the activity that the screen provides.
But, we feel that a review such as this is needed in order to emphasise the diverse influence that screens can have. 
If the results are not collated into a single place, it is difficult to see how the field will begin to progress away from 'screen time' as a concept. 
We have included this in the *Discussion* section:

@@

We also note that in reviewing the manuscript, we sometimes used the term 'screen time' and in other places used 'screen use'.
For the sake of being consistent, we have changed these to all be 'screen use' (which we think is more consistent with what is meant), and we also use this term for the rest of this letter.
This is just a stylistic change---we don't think that changing between 'time' and 'use' is what the reviewer means.

@@

The reviewer was pointing to the following quote from the *Lancet*: "Our understanding of the benefits, harms, and risks of our rapidly changing digital landscape is sorely lacking.".
It is not that the evidence is lacking, per se, but that our *understanding* is weak.
Our understanding is lacking partly because benefits of screen use (as seen in some educational literature) and reviewed separately from harms.
Our review aims to address this (see also Reviewer 1, \comment{r1_2}).
We think synthesising the trade-offs in one review can help us understand when screen use might be associated with good/poor outcomes, helping to better understand why.

@@

We appreciate it is not a direct contrast to compare overall limits of screen use against deleterious effects of screen use over 3-4 hours. As a result, we have removed the words 'in contrast':

@@

We agree that the relationship between some outcomes and screen use may not always be linear.
However, our previous research (e.g., 10.1186/s12966-019-0881-7) looking at a range of health and education outcomes in a high-quality dataset found little evidence for curvilinear relationships.
We therefore felt that the linear model was appropriate for the majority of the outcomes in this review.
Additionally, almost none of the reviews we included reported information that would allow us to calculate non-linear effects.
We agree that this is an important limitation though, and have added information on this to the *Discussion* section:

@@

We agree both guidelines focus on merely reducing recreational screen use and have removed "in all instances".
Even within recreational screen use, however, our findings do not support guidelines which focus just on minimisation. 
Video games, for example, are a recreational form of screen use which appear to have some benefits for educational and cognitive outcomes.
